\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-08-22 doc/sw-system.tex
Tweaks

However, it is not the case that only these small groups were capable of
making this large contribution: 9118 volunteers were ``experienced'' in that
they had all classified at least 10 training images; the 375 highest
contributing volunteers make up just 4\% of this experienced volunteer pool.
The cumulative distribution of agent skill is shown in
\Fref{fig:crowd:cumulskillplot}: these distributions are significantly broader
than the corresponding distributions of agent contribution in 
\Fref{fig:crowd:cumulplot}. The most skilled 20\% of agents possess only  79\%
of the skill at stage 1, and 77\% at stage 2. The inexperienced volunteers
also possess a significant fraction of the skill: the most skillful 20\% of
experienced volunteers (1824 people)  possess just 43\% of the total skill.
The level of contribution made at \sw by experienced volunteers is largely a
matter of choice (or perhaps, availability of time!).

>>>>

However, it is not the case that only these small groups were capable of
making this large contribution.
% : 9118 volunteers were ``experienced'' in that
% they had all classified at least 10 training images; the 375 highest
% contributing volunteers make up just 4\% of this experienced volunteer pool.
The cumulative distribution of agent skill is shown in
\Fref{fig:crowd:cumulskillplot}: these distributions are significantly broader
than the corresponding distributions of agent contribution in 
\Fref{fig:crowd:cumulplot}. The most skilled 20\% of agents possess only  79\%
of the skill at stage 1, and 77\% at stage 2. The inexperienced volunteers
also possess a significant fraction of the skill: the most skillful 20\% of
experienced volunteers (1824 people)  possess just 43\% of the total skill.
The level of contribution made at \sw by experienced volunteers is largely a
matter of choice (or perhaps, availability of time!).
